\item Consider the general nonlinear optimization problem

  \[
    \begin{aligned}
      \min \quad & f(x) & \\
      \textrm{s.t.} \quad & g_i(x) \le 0 \quad & i=1,\ldots,m \\
                          & h_i(x) = 0 \quad & i=1,\ldots,p.
    \end{aligned}
  \] 

  \begin{enumerate}[label=(\alph*)]
    \item Write down the Lagrangian.

      \medskip\textbf{Solution.}
      \[
      L(x, \lambda, \mu) = f(x) + \lambda^T h(x) + \mu^T g(x)
      .\] 

    \item Write down the dual function.

      \medskip\textbf{Solution.}
      \[
      q(\lambda,\mu) = \inf_{x \in \mathbb{R}^n} L(x,\lambda,\mu)
      .\] 

    \item Write down the dual problem.

      \medskip\textbf{Solution.}
      \[
        \begin{aligned}
          \max \quad & q(\lambda,\mu) \\
          \textrm{s.t.} \quad & \mu\ge 0 \\
        \end{aligned}
      \] 

    \item Explain weak duality. Show that weak duality always holds.

      \medskip\textbf{Solution.} The term weak duality refers to the fact that the
      optimal cost of the dual problem is always a lower bound of the optimal
      cost of the primal problem. To show this, let $x$ be any primal feasible
      point and $(\lambda,\mu)$ any dual feasible point. Then:
      \[
        q(\lambda, \mu) \le 
        L(x, \lambda, \mu) = 
        f(x) + \lambda^T h(x) + \mu^T g(x) \underbrace{=}_{\text{$h(x)=0,\mu\ge 0,g(x)\le 0$}}
        f(x)
      .\] 

      It suffices now to take infimums over dual and primal feasible points.

    \item Explain what is strong duality. Suppose that all functions are convex.
      Give a sufficient condition under which strong duality holds.

       \medskip\textbf{Solution.} Strong duality refers to the condition
       $d^*=p^*$, where $d^*$ is the optimal cost of the dual problem and $p^*$
       the optimal cost of the primal problem. This does not always hold, but
       when all functions are convex then Slater's condition is sufficient for
       strong duality to hold. In this case, each $h_i$ should be affine, and
       that there should exist a feasible vector $\overline{x}$ such that
       $g_i(\overline{x})<0$ for each non-affine $g_i$.

  \end{enumerate}
